Omics-based Single Step Trait Prediction

### 2017-09-14 paper/manuscript.tex
paper-intro, update population structure text

\Genetics2level{Population structure}
Population structure in Exp1 was examined by running a STRUCTURE
\cite{Pritchard2000} analysis with the number of putative ancestral
populations $K$ ranging from 2 to 9.
Based on the estimated probability of the data for each $K$, we chose $K=4$
and ran a principal component analysis (PCA) on the scaled and centered
genomic feature matrix using the \emph{pca} function from the \emph{R}-package
\emph{LEA} \cite{Frichot2015}.
Least-squares estimates of ancestry proportions were estimated based on sparse 
nonnegative matrix factorization algorithms~\cite{Frichot2014} using the 
\emph{snmf} function in \emph{LEA}.
Genotypes in the PCA plot (Fig.~\ref{fig:inbred-pca}) were colorized based on their
primary assignment to any of the four putative ancestral populations.
To avoid inflated predictive abilities, which can arise from large differences
in the average performance of the different subpopulations
\cite{Windhausen2012}, we reduced the panel of inbred lines to those primarily
belonging to either cluster 1 or cluster 4 in Fig.~\ref{fig:inbred-pca}.
This reduction yielded 164 genotypes, 110 of which were covered by both, genomic
and transcriptomic data.

>>>>

\Genetics2level{Population structure}
Population structure in Exp1 was examined through a STRUCTURE
\cite{Pritchard2000} analysis with the number of putative ancestral
populations $K$ ranging from 2 to 9.
Based on the estimated probability of the data for each $K$, we chose $K=4$
and ran a principal component analysis (PCA) on the scaled and centered
genomic feature matrix using the \emph{pca} function from the \emph{R}-package
\emph{LEA}~\cite{Frichot2015}.
Least-squares estimates of ancestry proportions were estimated based on sparse 
nonnegative matrix factorization algorithms~\cite{Frichot2014} using the 
\emph{snmf} function in \emph{LEA}.
Genotypes in the PCA plot (Fig.~\ref{fig:inbred-pca}) were colorized based on their
primary assignment to any of the four putative ancestral populations.
To mitigate the possibility of inflated predictive abilities, which can arise
from large differences in the average performance of the different
subpopulations~\cite{Windhausen2012}, we reduced the panel of inbred lines to
those primarily belonging to either cluster 1 or cluster 4 in 
Fig.~\ref{fig:inbred-pca}.
This reduction yielded 164 genotypes, 110 of which were covered by both, genomic
and transcriptomic data.
